\textsc{HubbleCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-01-15 paper/main.tex

Observations corresponding to individual proposal IDs are queried through the Mikulski Archive for Space Telescopes (MAST) via the \package{Astroquery} interface. Products of type \texttt{PREVIEW} are filtered in, corresponding to preview postcard images. We note that these are not science-grade observations, but rather lower-resolution images useful for quick-look purposes; given the nature of associations we aim to learn, this is adequate for our purposes. A maximum of 20 images are downloaded per proposal ID, selected at random, in order to avoid biasing the model towards proposals with a larger number of observations and survey-style campaigns. Images are centered and resized to a resolution-per-side of 512 pixels before. Color previews (i.e., observations taken with multiple wavelength filters assigned to individual RGB channels) are manually excluded via a filename filter in order to maintain consistency across the dataset; models trained on datasets with color images included were observed to show worse performance on generalization metrics. If no appropriate images corresponding to an abstract are found, is is excluded from the dataset.

@@

>>>>

Observations corresponding to individual proposal IDs are queried through the Mikulski Archive for Space Telescopes (MAST) via the \package{Astroquery} interface. Products of type \texttt{PREVIEW} are filtered in, corresponding to preview postcard images. We note that these are not science-grade observations, but rather lower-resolution images useful for quick-look purposes; given the nature of associations we aim to learn, this is adequate for our purposes. A maximum of 20 images are downloaded per proposal ID, selected at random, in order to avoid biasing the model towards proposals with a larger number of observations and survey-style campaigns. Images are centered and resized to a resolution-per-side of 512 pixels before. Color previews (i.e., observations taken with multiple wavelength filters assigned to individual RGB channels) are manually excluded via a filename filter in order to maintain consistency across the dataset; models trained on datasets with color images included were observed to show worse performance on generalization metrics. If no appropriate images corresponding to an abstract are found, it is excluded from the dataset.

@@

We note that some fraction of the image-caption pairs in the constructed dataset will center instrumentation and/or calibration rather than primary scientific content. We choose to not filter out these pairs from our dataset, in order to have a larger sample of HST observations for the image encoder to leverage for adapting to the distinctive characteristics of Hubble images.
